Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Forecasting in the Swiss Alps

### 2016-01-18 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Michel's corrections.

\begin{equation}
\label{eq:S1}
S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
\end{equation}
where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values, the more similar the pressure fields.

@@

The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP). Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.

@@

The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP. The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP. The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}). The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP. The optimization improves thus even more the forecasts for days with significant precipitation than usual days.

>>>>

\begin{equation}
\label{eq:S1}
S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
\end{equation}
where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values, the more similar the pressure fields.

@@

The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP). Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method. Parameters determined on the CP are then applied to the VP in order to obtain a performance score for the independent period.

@@

The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP. The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP. The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}). The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP. The optimization improves thus even more the forecasts for days with significant precipitation than usual days.
